\cvsection{Work Experience}

\begin{cventries}

  \cventry
    {Software Development Engineer} % Job title
    {\href{https://aws.amazon.com}{Amazon Web Services}} % Organization
    {Arlington, VA} % Location
    {October 2019 - Present} % Date(s)
    {
      \begin{cvitems}
      \end{cvitems}
    }

  \cventry
    {Software Engineer}
    {\href{https://www.vertafore.com}{Vertafore}}
    {East Lansing, MI}
    {April 2019 - October 2019}
    {
      \begin{cvitems}
        \item {Developed and maintained Java web applications for insurance and securities clients.}
        \item {Migrated existing architecture and source code to a static Angular codebase.}
        \item {Designed and implemented an SQL database for user authentication.}
        \item {Overhauled infrastructure to utilize serverless computational architecture, improving scalability.}
      \end{cvitems}
    }

  \cventry
    {Founder}
    {\href{https://better-games.org}{Better Games LLC}}
    {East Lansing, MI}
    {November 2018 - October 2019}
    {
      \begin{cvitems}
        \item {Designed and implemented the C\# backend and netcode for communication with Steam.}
        \item {Managed publisher communications and handled legal documentation for company formation.}
      \end{cvitems}
    }

  \cventry
    {Developer}
    {Michigan State University School of Planning, Design and Construction}
    {East Lansing, MI}
    {February 2019 - April 2019}
    {
      \begin{cvitems}
        \item {Utilized ArcGIS to display vacancy data statistics on a PHP-based website.}
        \item {Developed a login plugin with user management for the WordPress CMS.}
      \end{cvitems}
    }

  \cventry
    {Technical Assistant}
    {\href{https://icer.msu.edu}{Michigan State University Institute for Cyber-Enabled Research}}
    {East Lansing, MI}
    {July 2017 - February 2019}
    {
      \begin{cvitems}
        \item {Wrote build scripts and maintained packages for the High-Performance Computing Cluster (HPCC).}
        \item {Upgraded systems to a new node cluster, improving computational efficiency.}
      \end{cvitems}
    }

  \cventry
    {Web Developer}
    {\href{http://www.rsgis.msu.edu}{Michigan State University RS\&GIS}}
    {East Lansing, MI}
    {November 2015 - March 2017}
    {
      \begin{cvitems}
        \item {Developed the admissions portal and course registration system for the MSU College of Social Work.}
        \item {Maintained the course registration website for the MSU School of Human Resources and Labor Relations.}
      \end{cvitems}
    }

  \cventry
    {Research Assistant}
    {\href{https://prl.natsci.msu.edu/}{Michigan State University Plant Research Laboratory}}
    {East Lansing, MI}
    {December 2012 - January 2015}
    {
      \begin{cvitems}
        \item {Collaborated on projects involving Visual Phenomics, an image recognition system for analyzing photosynthetic data of plants.}
        \item {Developed PhenoMath, a tool for analyzing Visual Phenomics output using pattern recognition and outlier detection algorithms.}
      \end{cvitems}
    }

\end{cventries}
