\cvsection{Projects}

\begin{cventries}

  % Project 1
  \cventry
    {CMS used by insurance and securities companies to maintain appointments and aggregate data.}
    {CMS G2}
    {}
    {2019}
    {
      \begin{cvitems}
        \item {Developed in Java with an LDAP user system for authentication.}
        \item {Integrated with AWS for cloud-based data storage and processing.}
        \item {Streamlined appointment management and data aggregation for clients.}
      \end{cvitems}
    }

  % Project 2
  \cventry
    {Online multiplayer mini golf game distributed via Steam.}
    {\href{https://store.steampowered.com/app/1002650/Puttin_Around/}{Puttin' Around}}
    {}
    {2019}
    {
      \begin{cvitems}
        \item {Developed in C\# using the Unity engine.}
        \item {Implemented dedicated servers for seamless multiplayer gameplay.}
        \item {Achieved distribution on Steam, reaching a wide audience.}
      \end{cvitems}
    }

  % Project 3
  \cventry
    {Application system for MSU students to apply to the School of Social Work.}
    {MSU Social Work Undergraduate Application System}
    {}
    {2017}
    {
      \begin{cvitems}
        \item {Built with PHP and a MySQL database for efficient data management.}
        \item {Included an administration portal for managing applications (not publicly available).}
        \item {Simplified the application process for students and administrators.}
      \end{cvitems}
    }

  % Project 4
  \cventry
    {Web-based course registration system for MSU's School of HRLR.}
    {MSU School of Human Resources and Labor Relations Course Registration}
    {}
    {2017}
    {
      \begin{cvitems}
        \item {Developed in PHP with a MySQL backend for dynamic data handling.}
        \item {Provided an intuitive interface for students to register for courses.}
        \item {Improved administrative efficiency by automating registration workflows.}
      \end{cvitems}
    }

\end{cventries}